Hierarchical Dispatching and Overriding

### 2017-10-09 NewVersion/sections/Formalization.tex
S2. DrawableSafeDeck figure

There are two typing rules for method invocation: \textsc{(T-Invk)}
and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement
for a normal method invocation. First it ensures that the method
receiver $e_0$ type checks to a type $I_0$. Then it checks the type of
the specific method, by using an auxiliary function $\mbody(m, I_0,
I_0)$, which is the function for looking up methods that we will
illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
\mbody is different to FJ\bruno{Use xspace to fix the spacing problem
  of macros like mbody}, which has two parameters. The first $I_0$
represents the dynamic type and the second, the static type. If the
result of \mbody is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given. After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$. \textsc{(T-PathInvk)} is the typing judgement for a path invocation. Besides the conditions of \textsc{(T-Invk)}, \textsc{(T-PathInvk)} requires the type of receiver to be the subtype of the specified path type. 
% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

@@

\bruno{Well, there are two conditions. I suggest you explain
  in a bit more detail the 2 conditions, since this rule seems to be
  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} 
Rule \textsc{(T-Intf)} defines the typing rule for interfaces. Interface $I$ type checks only if the following conditions are satisfied: 1) all methods $\overline{M}$ that are directly defined in $I$ type check; 2) method lookup $\mbody(m, I, J)$ successes as long as the method $m$ is defined in any interface $J$ which is an ancestor of $I$; 3)if an original method $m$ defined in interfaces $I$ overrides another original method defined in an ancestor of $I$, then the method types are compatible. These conditions ensure unambiguity and type soundness of the calculus. We will introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime in any case. The interface check is responsible for capturing ambiguity during compilation.

\bruno{Explanation for T-Anno is missing}
Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation. The rule says that an annotated expression $\angl{J}e$ type checks to $J$ if the expression $e$ type checks and the static annotation $J$ is a subtype of $I$ which is the type of $e$.

>>>>

There are two typing rules for method invocation: \textsc{(T-Invk)}
and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement
for a normal method invocation. First it ensures that the method
receiver $e_0$ type checks to a type $I_0$. Then it checks the type of
the specific method, by using an auxiliary function $\mbody(m, I_0,
I_0)$, which is the function for looking up methods that we will
illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
\mbody{} is different to FJ\bruno{Use xspace to fix the spacing problem
  of macros like mbody}, which has two parameters. The first $I_0$
represents the dynamic type and the second, the static type. If the
result of \mbody is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given. After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$. \textsc{(T-PathInvk)} is the typing judgement for a path invocation. Besides the conditions of \textsc{(T-Invk)}, \textsc{(T-PathInvk)} requires the type of receiver to be the subtype of the specified path type. 
% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

@@

\bruno{Well, there are two conditions. I suggest you explain
  in a bit more detail the 2 conditions, since this rule seems to be
  the more complex one. Some examples may help.} \yanlin{added} 
Rule \textsc{(T-Intf)} defines the typing rule for interfaces. Interface $I$ type checks only if the following conditions are satisfied: 1) all methods $\overline{M}$ that are directly defined in $I$ type check; 2) method lookup $\mbody(m, I, J)$ successes as long as the method $m$ is originally defined in any interface $J$ which is an ancestor of $I$; 3)if an original method $m$ defined in interfaces $I$ overrides another original method defined in an ancestor of $I$, then the method types are compatible. These conditions ensure unambiguity and type soundness of the calculus. We will introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime in any case. The interface check is responsible for capturing ambiguity during compilation.

\bruno{Explanation for T-Anno is missing.}\yanlin{Added.}
Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation. The rule says that an annotated expression $\angl{J}e$ type checks to $J$ if the expression $e$ type checks and the static annotation $J$ is a subtype of $I$ which is the type of $e$.

### 2017-10-09 NewVersion/sections/Overview.tex
Section 4
S2. DrawableSafeDeck figure

@@

interface Drawable {
  JFrame draw() { // draws something on the screen
    JFrame frame = new JFrame();
    frame.setVisible(true);
    return frame;
  }
}
\end{lstlisting}\vspace{3pt}
Note that the two \lstinline|draw| methods have the same names and parameter types,
but the return types can be different. In \lstinline|Deck|,
\lstinline|draw| uses \lstinline|println|, which is a
library function. 
The method returns \lstinline|void|. Note that \lstinline|void| is
unsupported in our formalization, but we could have also defined an interface called \lstinline|Void|
and return an object of that type instead. For the method \lstinline|draw| in
\lstinline|Drawable|
the program has to create a blank canvas by \lstinline|JFrame|, which
is a pre-defined type.
\begin{comment}
\vspace{3pt}\begin{lstlisting}
interface JFrame {
  void setVisible(boolean b) {...}
  ...
}
\end{lstlisting}\vspace{3pt}
\end{comment}
Now, a programmer is designing a
card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
deck using multiple inheritance:

@@

\vspace{3pt}\begin{lstlisting}
interface SafeDeck extends Deck {
  boolean isEmpty() {...}
  void draw() { // overriding
    if (isEmpty()) println("The deck is empty.");
    else println("Draw a card");
  }
}
\end{lstlisting}\vspace{3pt}
With static dispatch, we have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
for the adaptation to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would take us back to problem
1, for instance, when we
have the UML in Figure~\ref{fig:drawableloggingdeck} and the following code:

\begin{figure*}[t]
	\saveSpaceFig
	\centering
	\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
	\caption{UML graph for \lstinline|DrawableLoggingDeck|.}\label{fig:drawableloggingdeck}
	\saveSpaceFig
\end{figure*}

>>>>

%In the remainder of this section we show three problems that arize 
%from unintentional method conflicts. The first two problems

@@

interface Drawable {
  JFrame draw() { // draws something on the screen
    JFrame frame = new JFrame();
    frame.setVisible(true);
    return frame;
  }
}
\end{lstlisting}\vspace{3pt}
Note that the two \lstinline|draw| methods have the same names and parameter types,
but the return types can be different. In \lstinline|Deck|,
\lstinline|draw| uses \lstinline|println|, which is a
library function. 
The method returns \lstinline|void|. Note that \lstinline|void| is
unsupported in our formalization, but we could have also defined an interface called \lstinline|Void|
and return an object of that type instead. For the method \lstinline|draw| in
\lstinline|Drawable|
the program has to create a blank canvas by \lstinline|JFrame|, which
is a pre-defined type.
\begin{comment}
\vspace{3pt}\begin{lstlisting}
interface JFrame {
  void setVisible(boolean b) {...}
  ...
}
\end{lstlisting}\vspace{3pt}
\end{comment}
Now, a programmer is designing a
card game with a GUI. He may want to draw a deck on the screen, so he defines a drawable
deck using multiple inheritance:

@@

\vspace{3pt}\begin{lstlisting}
interface SafeDeck extends Deck {
  boolean isEmpty() {...}
  void draw() { // overriding
    if (isEmpty()) println("The deck is empty.");
    else println("Draw a card");
  }
}
\end{lstlisting}\vspace{3pt}
With static dispatch, we have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
for the adaptation to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would take us back to problem
1, for instance, when we
have the UML in Figure~\ref{fig:drawablesafedeck} and the following code:

\begin{figure*}[t]
	\saveSpaceFig
	\centering
	\includegraphics[height=2cm]{pics/DrawableSafeDeck.pdf}
	\caption{UML graph for \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
	\saveSpaceFig
\end{figure*}
